% This file is called up by main.tex
% content in this file will be fed into the main document
% Thesis Abstract -----------------------------------------------------

%\begin{abstractslong}    %uncommenting this line gives a different abstract heading
\begin{abstracts}        % This creates the heading for the abstract page

The successful incubation of chicken eggs requires precise control of environmental conditions throughout the entire process. This proposal for a thesis aims to investigate how the Nordic Semiconductor Thingy:53, an IoT device equipped with a range of internal sensors, can be utilized to optimize and automate the management of egg-hatch environments. The research will utilize Thingy:53’s BME688 sensor to monitor temperature, humidity, pressure, and gas (air quality) and the BH1749 light sensor to detect light levels. The goal is to develop a reliable real-time monitoring and control system by reducing human intervention through automated data collection, real-time alerts, and comprehensive data analytics, ultimately enhancing hatch rates and operational efficiency. Machine learning algorithms will predict optimal hatching conditions based on historical data, enabling proactive adjustments to the incubation environment. Integrating with cloud platforms will allow long-term data storage and advanced analytics, providing valuable insights for ongoing improvement. This study will assess the effectiveness of Thingy:53 in maintaining optimal hatching conditions and its potential as a cost-effective, sustainable tool in poultry operations. The results will contribute to the advancement of smart agricultural practices and lay the groundwork for future innovations in the industry.

\end{abstracts}
%\end{abstractlongs}
% ---------------------------------------------------------------------- 