% This file is called up by main.tex
% content in this file will be fed into the main document
% Thesis acknowledgements -----------------------------------------------------

\begin{acknowledgements} % This creates the heading for the acknowledgements

\noindent   I would like to express my deepest gratitude to everyone who has supported me throughout this project. First and foremost, I would like to thank my supervisors, Prof. Dr. Tiziana Margaria and Amandeep Singh, for their invaluable guidance, encouragement, and expertise, which have been instrumental in shaping this work. Your patience and insightful feedback have genuinely enriched this study. \par \vspace*{1ex}

I would also like to extend my heartfelt thanks to my wife, Rizki Amalia, for her unwavering support, understanding, and love throughout this journey. Her encouragement and belief in me have been a constant source of strength, especially during the most challenging moments of this project. \par \vspace*{1ex}

Additionally, I would like to acknowledge my colleagues and peers in the Master of Science in Artificial Intelligence and Machine Learning 2023 for their constructive discussions and feedback. \par \vspace*{1ex}

Lastly, I want to recognize the Department of Computer Science and Information Systems, Faculty of Science and Engineering, University of Limerick, for providing the necessary resources and support that made this project possible. \par \vspace*{1ex}

Thank you all for your significant contributions to this work.




\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------